The Ecology of Cloud Computing

### 2022-04-07 paper.tex
Improved introduction and conclusion

In regards to the climate emergency, 'the cloud' is a rather apt metaphor for network computing; we are yet to learn whether it will provide us shade from a burning issue, or stand as an omen for a terrible storm. It has the potential to reduce the climate impact of several industries, but if not managed carefully it could cause our global emissions to skyrocket. This report will survey the current climate impact of scientific computing, the benefits of moving to the cloud from an environmental standpoint, and how to mitigate the impact of computing on our environment.

@@

Thus, it shouldn't be all or nothing; we should make a careful assessment of where we can reduce our energy use, and where we cannot. We should let it sway our judgements and play a factor in our science and scientific software. That way, it is possible to use the technology of the 'information age' in a way that is beneficial for both people and the planet.

>>>>

In regards to the climate emergency, 'the cloud' is a rather apt metaphor for network computing; we are yet to learn whether it will provide us shade from a burning issue, or stand as an omen for a terrible storm. It has the potential to reduce the climate impact of several industries, but if not managed carefully it could cause our global emissions to skyrocket. This report will survey the current climate impact of scientific computing with case studies in particular pertinent areas and parts of scientific computing workflows, taking a particular focus on cloud computing and how we can take a variety of approaches to mitigate the extra overhead introduced by cloud facilities, finishing with a discussion on some present and future ideas on how to reduce our climate impact. \newline

This is a topic I have chosen due to my interest in sustainability, and noting that there is thus far very little research and discussion into the impact of computing on the environment; it is often seen as something which just happens on the screen and has no real existence outside the machine's case. Leading the current research into the field is Lo{\"\i}c Lannelongue, from whose work much of my understanding and research into the topic germinated; his contribution to a digestible and layman-friendly yet uncompromising introduction to the field is invaluable.

@@

Thus, it shouldn't be all or nothing; we should make a careful assessment of where we can reduce our energy use, and where we cannot. I try to evoke a future where we let the environment sway our judgements and play a factor in our science and scientific software. That way, it is possible to use the technology of the 'information age' in a way that is beneficial for both people and the planet.
